On the Dynamics of Anthropomorphism in Robotics

### 2013-07-08 dynamics-anthropomorphism.tex
Added a section in discussion on experimental cues of anthropomorphism

>>>>

\subsection{Behavioral cues of anthropomorphism}
\label{sec:behavioralcues}

Our model suggests to analyze anthropomorphism based on a \emph{relative and
normalized level of anthropomorphic effects} instead of an absolute
quantitative assessment of anthropomorphic evidences. Similarly we introduce
two specific \emph{abstract} levels of anthropomorphism, the \emph{Initial
Capital of Anthropomorphism} and the \emph{Stabilized Level of
Anthropomorphism}: while we discuss the factors on which those values are
build, we did not formally investigated the experimental cues or evidences
that would allow to actually quantify those levels.

This is explained by the intricacy and interdependency of those behaviors.
Their correct identification and interpretation rely on psychosomatic cues that
the authors did not investigate.

A formal methodology for the assessment of anthropomorphic effects in HRI, as
well as a typology of these effects is still to be devised.
